---
title: "Ruth Gates GP Recalibration Accuracy"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load all of the needed libraries.

```{r}

#install.packages("nationalparkcolors")

# Graphical tools :
library(ggplot2)
library(cowplot)
#library(nationalparkcolors)

# Data Wrangling :
library(dplyr)
library(tidyr)
library(forcats)
library(car)
library(naniar)

```

## Read in GP recalibrated data, reformat and compare

```{r}
#read in table making separate columns for sample and genotype
chrN_LoCoGPr<-read.table(text = gsub("=|,","\t",readLines("~/Dropbox/CarlsLab/ResearchProjects/NOAA_RuthGates/GenomeAnalysis/GP_RecalibrationAccuracy/OZ034934.1_LoCoGPrecalSitesInfoAll.txt"))) 

head(chrN_LoCoGPr)
str(chrN_LoCoGPr)  

chrN_LoCoGPr<-chrN_LoCoGPr %>%  #convert genotype notation to numeric dosage
  mutate(across(everything(), ~replace(., . == '0/0', 0))) %>% 
  mutate(across(everything(), ~replace(., . == '0/1', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1/0', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1/1', 2))) %>% 
  mutate(across(everything(), ~replace(., . == './.', NA)))

chrN_LoCoGPr<-chrN_LoCoGPr %>% #make genotype/GP columns numeric
  mutate_at(c('V6', 'V8','V10', 'V12','V14', 'V16','V18', 'V20','V22', 'V24','V26', 'V28',"V30","V32", "V34", "V35", "V36", "V38" ,"V39", "V40", "V42", "V43", "V44", "V46", "V47", "V48", "V50", "V51","V52" ,"V54", "V55", "V56", "V58", "V59", "V60", "V62", "V63", "V64", "V66" ,"V67", "V68", "V70", "V71", "V72", "V74", "V75", "V76", "V78", "V79",  "V80", "V82", "V83","V84","V86","V87","V88"), as.numeric)

summary(chrN_LoCoGPr)

chrN_LoCoGPr_GT<-chrN_LoCoGPr %>% #pull out genotypes, Gprobs and ID columns
  select('V1','V2','V3','V4', 'V6', 'V8','V10', 'V12','V14', 'V16','V18', 'V20','V22', 'V24','V26', 'V28',"V30","V32", "V34", "V35", "V36", "V38" ,"V39", "V40", "V42", "V43", "V44", "V46", "V47", "V48", "V50", "V51","V52" ,"V54", "V55", "V56", "V58", "V59", "V60", "V62", "V63", "V64", "V66" ,"V67", "V68", "V70", "V71", "V72", "V74", "V75", "V76", "V78", "V79",  "V80", "V82", "V83","V84","V86","V87","V88")

head(chrN_LoCoGPr_GT)

#rename
namesLo<-c(CHROM="V1", POS="V2",ID="V3",AF="V4",GT_AP54="V6" ,GT_AP55="V8" ,GT_AP56="V10",GT_AP63="V12",GT_AP75="V14",GT_AP76="V16" ,GT_AP79="V18",GT_AP86= "V20" ,GT_AP89="V22",GT_AP91="V24" ,GT_AP30="V26",GT_AP14="V28",GT_AP8= "V30",GT_AP327= "V32",GPAA_AP54="V34",GPAB_AP54="V35", GPBB_AP54="V36", GPAA_AP55="V38", GPAB_AP55="V39" ,GPBB_AP55="V40",GPAA_AP56= "V42", GPAB_AP56="V43", GPBB_AP56="V44",GPAA_AP63= "V46",GPAB_AP63=  "V47",GPBB_AP63=  "V48", GPAA_AP75= "V50",GPAB_AP75= "V51",GPBB_AP75= "V52",GPAA_AP76="V54" ,GPAB_AP76="V55", GPBB_AP76="V56",GPAA_AP79= "V58", GPAB_AP79="V59",GPBB_AP79= "V60", GPAA_AP86="V62", GPAB_AP86="V63",GPBB_AP86= "V64", GPAA_AP89="V66", GPAB_AP89="V67" ,GPBB_AP89="V68", GPAA_AP91="V70", GPAB_AP91="V71", GPBB_AP91="V72", GPAA_AP30="V74", GPAB_AP30="V75", GPBB_AP30="V76", GPAA_AP14="V78",GPAB_AP14= "V79",GPBB_AP14= "V80", GPAA_AP8= "V82", GPAB_AP8="V83", GPBB_AP8="V84", GPAA_AP327= "V86", GPAB_AP327="V87", GPBB_AP327="V88")

chrN_LoCoGPr_GT<-rename(chrN_LoCoGPr_GT, namesLo)

head(chrN_LoCoGPr_GT)

chrN_LoCoGPr_GTL<-chrN_LoCoGPr_GT %>% #reformat to tidy 
  pivot_longer(
    cols = starts_with("G"),
    names_to = c("Info","Genet"),
    names_sep = "_",
    values_to = "LoCoGPr",
    values_drop_na = TRUE
  ) %>%
  pivot_wider(names_from = "Info",values_from = "LoCoGPr")%>%
  filter(Genet!="AP79") # AP79 tossed from HiCo dataset

head(chrN_LoCoGPr_GTL)

```

## pull in high coverage 'truth' dataset and determine how many loci were genotyped

```{r}


chrN_HiCoGPr<-read.table(text = gsub("=|,","\t",readLines("~/Dropbox/CarlsLab/ResearchProjects/NOAA_RuthGates/GenomeAnalysis/GP_RecalibrationAccuracy/OZ034934.1_HiCoGPrecalSitesInfoAll.txt"))) 

head(chrN_HiCoGPr)
str(chrN_HiCoGPr) 

chrN_HiCoGPr<-chrN_HiCoGPr %>%  #convert genotype notation to numeric dosage
  mutate(across(everything(), ~replace(., . == '0/0', 0))) %>% 
  mutate(across(everything(), ~replace(., . == '0/1', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1/0', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1/1', 2))) %>% 
  mutate(across(everything(), ~replace(., . == './.', NA)))

chrN_HiCoGPr<-chrN_HiCoGPr %>% #make genotype columns numeric
  mutate_at(c('V5', 'V7','V9', 'V11','V13', 'V15','V17', 'V19','V21', 'V23','V25', 'V27',"V29","V31", "V33","V35","V37" ,"V39" ,"V41" ,"V43" ,"V45" ,"V47","V49" ,"V51" , "V53" , "V55","V57","V59"), as.numeric)

chrN_HiCoGPr_GT<-chrN_HiCoGPr %>% #pull out genotypes and read depth
  select('V1','V2','V3', 'V5', 'V7','V9', 'V11','V13', 'V15','V17', 'V19','V21', 'V23','V25', 'V27',"V29","V31", "V33","V35","V37" ,"V39" ,"V41" ,"V43" ,"V45" ,"V47","V49" ,"V51" , "V53" , "V55","V57","V59")

#rename
namesHi<-c(CHROM="V1", POS="V2",ID="V3",AP54_GT="V5" ,AP55_GT="V7" ,AP56_GT="V9",AP63_GT="V11",AP75_GT="V13",AP76_GT="V15" ,AP79_GT="V17",AP86_GT= "V19" ,AP89_GT="V21",AP91_GT="V23" ,AP30_GT="V25",AP14_GT="V27",AP8_GT= "V29",AP327_GT= "V31",AP54_DP="V33" ,AP55_DP="V35" ,AP56_DP="V37",AP63_DP="V39",AP75_DP="V41",AP76_DP="V43" ,AP79_DP="V45",AP86_DP= "V47" ,AP89_DP="V49",AP91_DP="V51" ,AP30_DP="V53",AP14_DP="V55",AP8_DP= "V57",AP327_DP= "V59")

chrN_HiCoGPr_GT<-rename(chrN_HiCoGPr_GT, namesHi)

head(chrN_HiCoGPr_GT)


chrN_HiCoGPr_GTL<-chrN_HiCoGPr_GT %>% #pivot all genotype to single col
  pivot_longer(
    cols = starts_with("AP"),
    names_to = c("Genet","Info"),
    names_sep = "_",
    values_to = "HiCoGPr",
    values_drop_na = TRUE
  )%>%
  pivot_wider(names_from = "Info",values_from = "HiCoGPr")%>%
  filter(Genet!="AP79")


head(chrN_HiCoGPr_GTL)

```

## NOW join the two datasets by chromosome and position

```{r}


chrNval<-inner_join(chrN_LoCoGPr_GTL, chrN_HiCoGPr_GTL, 
           by = c("CHROM", "POS","Genet"))

head(chrNval)
summary(chrNval)

chrNval %>%
 mutate_at(vars(Genet), factor) %>% 
  group_by(Genet) %>%
  summarize(meanGPAA=mean(GPAA))

chrNval %>% # how many loci available for comparisson total
  distinct(ID.x) 

```

## how many loci available for comparisson total

#chr21: 152,035 #chr22: 102,180 #chr23: 106,729 #chr24: 98,522 #chr25: 97,721 #chr26: 102,756 #chr27: 89,000 #chr28: 87,306 #chr29: 104,767 #chr30: 86,090 #chr31: 82,739 #chr32: 100,549 #chr33: 94,194 #chr34: 94,186

```{r}

  
chrNval %>% # how many loci with different SNP IDs...note its not many; a couple just naming convention #some are different alleles between ref and alternate...some are flips in indels between ref and alternate
  filter(ID.x!=ID.y) %>% 
  distinct(ID.x,ID.y) 

chrNval %>%
  filter(ID.x!=ID.y) %>% 
  with(hist(AF)) #majority are lower AF 


```

## how many loci with different SNP IDs...

## note its not many; a couple just naming convention

#some are different alleles between ref and alternate...some are flips in indels between ref and alternate

#chr21: 80 loci\
#chr22: 47 loci #chr23: 42 loci #chr24: 51 loci #chr25: 54 loci #chr26: 48 loci #chr27: 42 loci #chr28: 49 loci #chr29: 64 loci #chr30: 53 loci #chr31: 51 loci #chr32: 44 loci #chr33: 53 loci #chr34: 57 loci

### lets focus on apples to apples loci for truth vs recal dataset comparison and generate plots of accuracy

```{r}

#first generate range of values across LoCo MAF bins

AF_005<-chrNval %>% #lets explore how much AF affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter for hi co dataset
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(AF < 0.05) %>% #set AF filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))


AF_01<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.05,0.15)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_02<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.15,0.25)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_03<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.25,0.35)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_04<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.35,0.45)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_05<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.45,0.55)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_06<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.55,0.65)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_07<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.65,0.75)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_08<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.75,0.85)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_09<-chrNval %>% 
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(between(AF,0.85,0.95)) %>% #set AF filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

AF_095<-chrNval %>% #lets explore how much AF affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter for hi co dataset
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(AF > 0.95) %>% #set AF filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoAF=mean(AF),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))
```

## Combine and plot

```{r}


chrNAccByMAF<-bind_rows(AF_005,AF_01,AF_02,AF_03,AF_04,AF_05,AF_06,AF_07,AF_08,AF_09,AF_095)

p1<-chrNAccByMAF %>%
ggplot(aes(x=LoCoAF, y=r2)) +
  geom_jitter()+
  geom_smooth()+
  theme_bw() + 
  xlab("Low Coverage MAF") + 
  ylab("Pearson's r2") +
  ylim(0,1.0)


p2<-chrNAccByMAF %>% #pivot all genotype to single col
  pivot_longer(
    cols = ends_with("Rate"),
    names_to = c("Genotype"),
    values_to = "Rate"
  )%>%
  ggplot(aes(x=LoCoAF, y=Rate, color=Genotype)) +
  geom_jitter()+
  geom_smooth() +
  theme_bw() + 
  xlab("Low Coverage MAF") + 
  ylab("Genotype Concordance") +
  ylim(0,1.0)+
  scale_color_manual(labels = c("Heterozygote", "Homozygous Alt","Homozygous Ref"), values = c("violet", "coral","lightblue"))

p3<-chrNAccByMAF %>% #pivot all genotype to single col
  pivot_longer(
    cols = ends_with("Sites"),
    names_to = c("Genotype"),
    values_to = "Nsites"
  )%>%
  ggplot(aes(x=LoCoAF, y=Nsites, color=Genotype)) +
  geom_jitter()+
  geom_smooth() +
  theme_bw() + 
  xlab("Low Coverage MAF") + 
  ylab("N Sites Genotyped") +
#  ylim(0,1.0)+
  scale_color_manual(labels = c("Heterozygote", "Homozygous Alt","Homozygous Ref"), values = c("violet", "coral","lightblue"))

```


## combine and generate final plot and 3 plot panel and a few summary tables

```{r}

plots1 <- list(p1, p2, p3)

plots1panel <- ggpubr::ggarrange(plotlist = plots1, nrow = 1, ncol = 3, labels = "AUTO",common.legend=TRUE,legend="bottom")

ggpubr::annotate_figure(plots1panel, top = ggpubr::text_grob("CHROMOSOME 34 - post GP recalibration", 
               color = "black", face = "bold", size = 14))

chrNAccByMAF %>% summarize(globalPearson=mean(r2,na.rm=TRUE))

#per chromosome Pearson R2 and 'global' mean
mean(c(0.878,0.878,0.871,0.883,0.834,0.854,0.862,0.878,0.876,0.859,0.849,0.850,0.865,0.879))

```

