---
title: "Ruth Gates Imputation Accuracy"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load all of the needed libraries.

```{r}

#install.packages("nationalparkcolors")

# Graphical tools :
library(ggplot2)
library(cowplot)
#library(nationalparkcolors)

# Data Wrangling :
library(dplyr)
library(tidyr)
library(forcats)
library(car)
library(naniar)

```

## Read in Imputed data, reformat and compare

```{r}
#read in table making separate columns for sample and genotype
chrN_LoCoIMP<-read.table(text = gsub("=|,","\t",readLines("~/Dropbox/CarlsLab/ResearchProjects/NOAA_RuthGates/GenomeAnalysis/ImputationAccuracy/OZ034934.1_LoCoImputedSitesInfoAll.txt"))) 

head(chrN_LoCoIMP)
str(chrN_LoCoIMP)  

chrN_LoCoIMP<-chrN_LoCoIMP %>%  #convert genotype notation to numeric dosage
  mutate(across(everything(), ~replace(., . == '0|0', 0))) %>% 
  mutate(across(everything(), ~replace(., . == '0|1', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1|0', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1|1', 2))) %>% 
  mutate(across(everything(), ~replace(., . == './.', NA)))

chrN_LoCoIMP<-chrN_LoCoIMP %>% #make genotype/GP columns numeric
  mutate_at(c('V7', 'V9','V11', 'V13','V15', 'V17','V19', 'V21','V23', 'V25','V27', 'V29',"V31","V33", "V35", "V36", "V37", "V39" ,"V40", "V41", "V43", "V44", "V45", "V47", "V48", "V49", "V51", "V52","V53" ,"V55", "V56", "V57", "V59", "V60", "V61", "V63", "V64", "V65", "V67" ,"V68", "V69", "V71", "V72", "V73", "V75", "V76", "V77", "V79", "V80",  "V81", "V83", "V84","V85","V87","V88","V89"), as.numeric)

summary(chrN_LoCoIMP)

chrN_LoCoIMP_GT<-chrN_LoCoIMP %>% #pull out genotypes, Gprobs and IDs
  select('V1','V2','V3','V4', 'V5','V7', 'V9','V11', 'V13','V15', 'V17','V19', 'V21','V23', 'V25','V27', 'V29',"V31","V33", "V35", "V36", "V37", "V39" ,"V40", "V41", "V43", "V44", "V45", "V47", "V48", "V49", "V51", "V52","V53" ,"V55", "V56", "V57", "V59", "V60", "V61", "V63", "V64", "V65", "V67" ,"V68", "V69", "V71", "V72", "V73", "V75", "V76", "V77", "V79", "V80",  "V81", "V83", "V84","V85","V87","V88","V89")

#rename
namesLo<-c(CHROM="V1", POS="V2",ID="V3",DR2="V4",AF="V5",GT_AP54="V7" ,GT_AP55="V9" ,GT_AP56="V11",GT_AP63="V13",GT_AP75="V15",GT_AP76="V17" ,GT_AP79="V19",GT_AP86= "V21" ,GT_AP89="V23",GT_AP91="V25" ,GT_AP30="V27",GT_AP14="V29",GT_AP8= "V31",GT_AP327= "V33",GPAA_AP54="V35",GPAB_AP54="V36", GPBB_AP54="V37", GPAA_AP55="V39", GPAB_AP55="V40" ,GPBB_AP55="V41",GPAA_AP56= "V43", GPAB_AP56="V44", GPBB_AP56="V45",GPAA_AP63= "V47",GPAB_AP63=  "V48",GPBB_AP63=  "V49", GPAA_AP75= "V51",GPAB_AP75= "V52",GPBB_AP75= "V53",GPAA_AP76="V55" ,GPAB_AP76="V56", GPBB_AP76="V57",GPAA_AP79= "V59", GPAB_AP79="V60",GPBB_AP79= "V61", GPAA_AP86="V63", GPAB_AP86="V64",GPBB_AP86= "V65", GPAA_AP89="V67", GPAB_AP89="V68" ,GPBB_AP89="V69", GPAA_AP91="V71", GPAB_AP91="V72", GPBB_AP91="V73", GPAA_AP30="V75", GPAB_AP30="V76", GPBB_AP30="V77", GPAA_AP14="V79",GPAB_AP14= "V80",GPBB_AP14= "V81", GPAA_AP8= "V83", GPAB_AP8="V84", GPBB_AP8="V85", GPAA_AP327= "V87", GPAB_AP327="V88", GPBB_AP327="V89")

chrN_LoCoIMP_GT<-rename(chrN_LoCoIMP_GT, namesLo)

head(chrN_LoCoIMP_GT)

chrN_LoCoIMP_GTL<-chrN_LoCoIMP_GT %>% #reformat to tidy 
  pivot_longer(
    cols = starts_with("G"),
    names_to = c("Info","Genet"),
    names_sep = "_",
    values_to = "LoCoIMP",
    values_drop_na = TRUE
  ) %>%
  pivot_wider(names_from = "Info",values_from = "LoCoIMP")%>%
  filter(Genet!="AP79")



```

## pull in high coverage truth dataset and determine how many loci were genotyped

```{r}


chrN_HiCoIMP<-read.table(text = gsub("=|,","\t",readLines("~/Dropbox/CarlsLab/ResearchProjects/NOAA_RuthGates/GenomeAnalysis/ImputationAccuracy/OZ034934.1_HiCoImputedSitesInfoAll.txt"))) 

head(chrN_HiCoIMP)
str(chrN_HiCoIMP) # fewer sites reliably genotyped, as expected 45844

chrN_HiCoIMP<-chrN_HiCoIMP %>%  #convert genotype notation to numeric dosage
  mutate(across(everything(), ~replace(., . == '0/0', 0))) %>% 
  mutate(across(everything(), ~replace(., . == '0/1', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1/0', 1))) %>% 
  mutate(across(everything(), ~replace(., . == '1/1', 2))) %>% 
  mutate(across(everything(), ~replace(., . == './.', NA)))

chrN_HiCoIMP<-chrN_HiCoIMP %>% #make genotype columns numeric
  mutate_at(c('V5', 'V7','V9', 'V11','V13', 'V15','V17', 'V19','V21', 'V23','V25', 'V27',"V29","V31", "V33","V35","V37" ,"V39" ,"V41" ,"V43" ,"V45" ,"V47","V49" ,"V51" , "V53" , "V55","V57","V59"), as.numeric)

chrN_HiCoIMP_GT<-chrN_HiCoIMP %>% #pull out genotypes and IDs
  select('V1','V2','V3', 'V5', 'V7','V9', 'V11','V13', 'V15','V17', 'V19','V21', 'V23','V25', 'V27',"V29","V31", "V33","V35","V37" ,"V39" ,"V41" ,"V43" ,"V45" ,"V47","V49" ,"V51" , "V53" , "V55","V57","V59")

#rename
namesHi<-c(CHROM="V1", POS="V2",ID="V3",AP54_GT="V5" ,AP55_GT="V7" ,AP56_GT="V9",AP63_GT="V11",AP75_GT="V13",AP76_GT="V15" ,AP79_GT="V17",AP86_GT= "V19" ,AP89_GT="V21",AP91_GT="V23" ,AP30_GT="V25",AP14_GT="V27",AP8_GT= "V29",AP327_GT= "V31",AP54_DP="V33" ,AP55_DP="V35" ,AP56_DP="V37",AP63_DP="V39",AP75_DP="V41",AP76_DP="V43" ,AP79_DP="V45",AP86_DP= "V47" ,AP89_DP="V49",AP91_DP="V51" ,AP30_DP="V53",AP14_DP="V55",AP8_DP= "V57",AP327_DP= "V59")

chrN_HiCoIMP_GT<-rename(chrN_HiCoIMP_GT, namesHi)

head(chrN_HiCoIMP_GT)


chrN_HiCoIMP_GTL<-chrN_HiCoIMP_GT %>% #pivot all genotype to single col
  pivot_longer(
    cols = starts_with("AP"),
    names_to = c("Genet","Info"),
    names_sep = "_",
    values_to = "HiCoIMP",
    values_drop_na = TRUE
  )%>%
  pivot_wider(names_from = "Info",values_from = "HiCoIMP")%>%
  filter(Genet!="AP79")


head(chrN_HiCoIMP_GTL)

```

## NOW join the two datasets by chromosome and position

```{r}


chrNval<-inner_join(chrN_LoCoIMP_GTL, chrN_HiCoIMP_GTL, 
           by = c("CHROM", "POS","Genet"))

head(chrNval)
summary(chrNval)

chrNval %>%
 mutate_at(vars(Genet), factor) %>% 
  group_by(Genet) %>%
  summarize(meanGPAA=mean(GPAA))

chrNval %>% # how many loci available for comparisson total
  distinct(ID.x)

```

## how many loci available for comparisson total

#chr21: 45,318 #chr22: 34,301 #chr23: 32,924 #chr24: 28,551 #chr25: 31,082 #chr26: 30,344 #chr27: 35,781 #chr28: 24,072 #chr29: 30,874 #chr30: 25,551 #chr31: 24,640 #chr32: 29,102 #chr33: 27,994 #chr34: 25,843

```{r}

  
chrNval %>% # how many loci with different SNP IDs...note its not many; a couple just naming convention #some are different alleles between ref and alternate...some are flips in indels between ref and alternate
  filter(ID.x!=ID.y) %>% 
  distinct(ID.x,ID.y) 

chrNval %>%
  filter(ID.x!=ID.y) %>% 
  with(hist(AF)) #majority are low AF and would presumably be tossed anyway

chrNval %>%
  filter(ID.x!=ID.y) %>% 
  with(hist(DR2)) #but DR2 values are generally high

```

## how many loci with different SNP IDs...

## note its not many; a couple just naming convention

#some are different alleles between ref and alternate...some are flips in indels between ref and alternate

#chr21: 872 loci\
#chr22: 667 loci #chr23: 697 loci #chr24: 669 loci #chr25: 618 loci #chr26: 653 loci #chr27: 641 loci #chr28: 510 loci #chr29: 680 loci #chr30: 586 loci #chr31: 497 loci #chr32: 686 loci #chr33: 724 loci #chr34: 589 loci

### lets focus on apples to apples loci for truth vs imputation dataset comparison as a fcn of DR2 and generate plots of accuracy

```{r}

#first generate range of values across DR2s

DR_00<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
#  filter(DR2 > 0.50) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))


DR_01<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.10) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_02<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.20) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_03<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.30) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_04<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.40) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_05<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.50) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))
  

DR_06<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.60) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_07<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.70) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_08<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.80) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_09<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.90) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_095<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.95) %>% #set DR2 filter for LoCo dataset
   group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

DR_099<-chrNval %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  filter(ID.x==ID.y) %>% #apples to apples
  filter(DP>=10) %>% #depth filter
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT.x))%>% #ignore rows where GT has not been called
  filter(!is.na(GT.y))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.99) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(HiCoDP=min(DP),LoCoDR2=min(DR2),HomRefSites=sum(GT.y==0),HomRefConc=sum(GT.y==GT.x & GT.y==0),HetSites=sum(GT.y==1), HetConc=sum(GT.y==GT.x &GT.y==1),HomAltSites=sum(GT.y==2),HomAltConc=sum(GT.y==GT.x & GT.y==2),r2=cor(GT.x,GT.y,method="pearson",use="complete.obs"),HomRefConcRate=HomRefConc/HomRefSites,HetConcRate=HetConc/HetSites,HomAltConcRate=HomAltConc/HomAltSites,NsitesConcTotal=sum(HomRefConc,HetConc,HomAltConc))

```

## Combine and plot

```{r}


chrNAccByDR<-bind_rows(DR_00,DR_01,DR_02,DR_03,DR_04,DR_05,DR_06,DR_07,DR_08,DR_09,DR_095,DR_099)

p1<-chrNAccByDR %>%
ggplot(aes(x=LoCoDR2, y=r2)) +
  geom_jitter()+
  geom_smooth()+
  theme_bw() + 
  xlab("Low Coverage DR2") + 
  ylab("Pearson's r2") +
  ylim(0.50,1.0)+
  geom_vline(xintercept=0.99,col="red")


p2<-chrNAccByDR %>% #pivot all genotype to single col
  pivot_longer(
    cols = ends_with("Rate"),
    names_to = c("Genotype"),
    values_to = "Rate"
  )%>%
  ggplot(aes(x=LoCoDR2, y=Rate, color=Genotype)) +
  geom_jitter()+
  geom_smooth() +
  theme_bw() + 
  xlab("Low Coverage DR2") + 
  ylab("Genotype Concordance") +
  ylim(0.50,1.0)+
  scale_color_manual(labels = c("Heterozygote", "Homozygous Alt","Homozygous Ref"), values = c("violet", "coral","lightblue"))+
  geom_vline(xintercept=0.99,col="red")

```

## now final question is how many imputed loci would we retain in original shallow dataset over this range of DR2

```{r}

#again generate range of SNPs across DR2s

LoDR_00<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
#  filter(DR2 > 0.50) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_01<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.10) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_02<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.20) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_03<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.30) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_04<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.40) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_05<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.50) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))
  

LoDR_06<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.60) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_07<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.70) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_08<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.80) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_09<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.90) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_095<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.95) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))


LoDR_099<-chrN_LoCoIMP_GTL %>% #lets explore how much HiCo depth an GP affects concordance to determine "truth"
  mutate_at(vars(Genet), factor) %>% #make genet a factor for excluding outlier test
  filter(!is.na(GT))%>% #ignore rows where GT has not been called
  filter(DR2 >= 0.99) %>% #set DR2 filter for LoCo dataset
  group_by(Genet) %>%  
  summarize(LoCoDR2=min(DR2),HomRefSites=sum(GT==0),HetSites=sum(GT==1), HomAltSites=sum(GT==2),NsitesTotal=sum(HomRefSites,HetSites,HomAltSites))

```

## combine and generate final plot and 3 plot panel and a few summary tables

```{r}

chrNSitesByDR<-bind_rows(LoDR_00,LoDR_01,LoDR_02,LoDR_03,LoDR_04,LoDR_05,LoDR_06,LoDR_07,LoDR_08,LoDR_09,LoDR_095,LoDR_099)

p3<-chrNSitesByDR %>% ## FOR N SITES, NEED TO FIGURE OUT IN OG DATASET, no intersection, how many sites remain at these DR2 thresholds
ggplot(aes(x=LoCoDR2, y=NsitesTotal)) +
  geom_jitter()+
  geom_smooth()+
  theme_bw() + 
  xlab("Low Coverage DR2") + 
  ylab("N Genotyped Sites") +
  ylim(5000,120000)+
  geom_vline(xintercept=0.99,col="red")

plots1 <- list(p3, p1, p2)

plots1panel <- ggpubr::ggarrange(plotlist = plots1, nrow = 1, ncol = 3, labels = "AUTO",common.legend=TRUE,legend="bottom")

ggpubr::annotate_figure(plots1panel, top = ggpubr::text_grob("CHROMOSOME 34", 
               color = "black", face = "bold", size = 14))

chrNAccByDR %>%
  group_by(LoCoDR2) %>%
  summarize(MeanConcordanceHomRef=mean(HomRefConcRate),MeanConcordanceHomAlt=mean(HomAltConcRate),MeanConcordanceHet=mean(HetConcRate),MeanR2=mean(r2))

chrNSitesByDR %>%
  distinct(NsitesTotal)

```
#Total sites:
#DR2\>=0.99 #chr21: 13927 sites, 95-99% concordance, r2=0.93 #chr22: 9804 sites, 95-99% concordance, r2=0.94 #chr23: 10669 sites, 95-99% concordance, r2=0.93, #chr24: 9475 sites, 96-99% concordance, r2=0.949 #chr25: 9340 sites, 95-99% concordance, r2=0.914 - AP55 is big het outlier here #chr26: 10414 sites, 95-99% concordance, r2=0.92 #chr27: 10879 sites, 95-98 concordance, r2=0.92 #chr28: 7183 sites, #chr29: 9770 sites, #chr30: 7903 sites, #chr31: 6534 sites #chr32: 8152 sites #chr33: 8388 sites #chr34: 8627 sites

#LoCoDR2 MeanConcordanceHomRef MeanConcordanceHomAlt MeanConcordanceHet MeanR2 #0.99 0.953 0.990 0.972 0.932 #0.99 0.955 0.990 0.974 0.943 #0.99 0.953 0.987 0.976 0.931 #0.99 0.965 0.988 0.972 0.949 #0.99 0.952 0.990 0.958 0.914 #0.99 0.953 0.988 0.974 0.920 #0.99 0.965 0.982 0.951 0.920 #0.99 0.961 0.988 0.947 0.936 #0.99 0.959 0.987 0.975 0.944 #0.99 0.958 0.991 0.977 0.939 #0.99 0.951 0.990 0.974 0.924 #0.99 0.946 0.989 0.970 0.909 #0.99 0.959 0.988 0.974 0.948 #0.99 0.957 0.982 0.971 0.937


